---
title: "Codebook"
author: "Manav Kumar"
date: "February 25, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## CodeBook for "Getting and Cleaning Data" Course project

```{r eval=TRUE,echo = FALSE,results='hide'}
source("run_analysis.R")
```

The source data is obtained from 
https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip

A full description of the Data can be obtained from:

http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

For this analysis, the data cleanup has been achieved by the script run_analysis.R

* The training and test datasets are first individually loaded, joined with the subject and activity identifiers and tagged as "Train" or "Test" using obsType column
* When selecting the data only the variables that are mean and standard deviations of the observations were loaded to individual subsets
* The two datasets have been merged into a single dataset (activityData) using rbind
* The fields are:

```{r eval=TRUE,echo=TRUE}
names(activityData)

```


